---
title: "Week 04"
author: "Taylor Riley(mailto:striley@uw.edu)"
date: '`r format(Sys.time(), "%Y-%m-%d %H:%M")`'
output:
  bookdown::html_document2
---


```{r, include=F}
### -----------------------------------------------------------
# Set up
library(tidyverse)
library(magrittr)
library(kableExtra)
library(stargazer)
library(pander)
library(psych)
library(readstata13)
library(knitr)
library(animation)
library(bookdown)
library(rmarkdown)


```

Table of Contents 

A. Questions/Answers 
<p>&nbsp;</p>
B. Source Code for this document


<p>&nbsp;</p>

A. Questions/Answers 

Since we don't have answers back yet from HW 4, here is a practice commit for HW 5. 




```{r Q1, include = F}
### -----------------------------------------------------------
### Create data

gradpain <- c(rep(0,11), rep(1,1), rep(2,2), rep(3,6), rep(4,8), rep(5,10),
rep(6,8), rep(7,30), rep(8,10), rep(9,6), rep(10,2))

barplot(table(gradpain), las=1, ylab="Frequency", xlab="Pain Scale",
main="How painful is graduate school?")

# Get number of students 
gradpain <- data.frame(gradpain)
nrow(gradpain)

mean(gradpain$gradpain)


```

1. How many graduate students are in the sample?
<p>&nbsp;</p>

There are `r nrow(gradpain)` graduate students in the sample.

<p>&nbsp;</p>

2. What is the sample mean?
<p>&nbsp;</p>

The sample mean is `r mean(gradpain$gradpain) %>% round(2)`.

<p>&nbsp;</p>

```{r Q3, include = F}
### -----------------------------------------------------------
### Functions with bootstrap

# Create vector
gradpain.vec <- gradpain$gradpain

# Defining function with d.vec and n arguments
my_function <- function(d.vec, n) {
  
  sample <- sample(x = d.vec, size = n, replace = TRUE) 
  
  list <- list(
    sample_size = n,
    sample_mean = mean(sample)
  )
  
  return(list)
}

# Verifying the function works with data
my_function(d.vec = gradpain.vec, n = length(gradpain.vec))

# Loopin to run the function 100 times
my.function.samples <- rep(NA, 100)

set.seed(7)  # make your work reproducible

for(i in 1:100){
  
  my.list.results <- my_function(gradpain.vec, length(gradpain.vec))
  my.function.samples[i] <- my.list.results$sample_mean
}


# mean
mean(my.function.samples)

# SD
sd(my.function.samples)

 
```

3. What is the mean of these 100 means?
<p>&nbsp;</p>

The mean of these 100 means is `r mean(my.function.samples) %>% round(2)`. 

<p>&nbsp;</p>

4. What is the standard deviation of these 100 means?
<p>&nbsp;</p>

The standard deviation is `r sd(my.function.samples) %>% round(2)`.

<p>&nbsp;</p>


```{r Q5, include = F}
### -----------------------------------------------------------
### Functions with bootstrap

# Create vector
gradpain.vec <- gradpain$gradpain

# Defining function with d.vec and n arguments
my_function2 <- function(d.vec, n, num.samples) {
  
  sample <- sample(x = d.vec, size = n, replace = TRUE) 
  
  list <- list(
    sample_size = n,
    sample_mean = mean(sample),
    n = num.samples,
    sd = sd(sample),
    ll95 = mean(sample) - 1.96 * (sd(sample)/sqrt(n)),
    ul95 = mean(sample) + 1.96 * (sd(sample)/sqrt(n))
  )
  
  return(list)
  
  my.function.samples <- rep(NA, num.samples)
  for(i in 1:num.samples){
  
  my.list.results <- my_function(gradpain.vec, length(gradpain.vec))
  my.function.samples[i] <- my.list.results$sample_mean
}
  
}

# Verifying the function works with data
my_function2(d.vec = gradpain.vec, n = length(gradpain.vec), num.samples = 100)

 
```

5. What does your function return for the mean of means?
<p>&nbsp;</p>

The mean of means returned is 5.638.
<p>&nbsp;</p>

6. What does your function return for the standard deviation of means?
<p>&nbsp;</p>

The standard deviation of means is 2.56
<p>&nbsp;</p>


7. What does your function return for the 95% confidence interval around the mean?
<p>&nbsp;</p>

The 95% CI around the mean is (5.12, 6.16)
<p>&nbsp;</p>



## Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
