---
title: "Week 07"
author: "Taylor Riley(mailto:striley@uw.edu)"
date: '`r format(Sys.time(), "%Y-%m-%d %H:%M")`'
output:
  bookdown::html_document2
---


```{r setup, include=F}
### -----------------------------------------------------------
# Set up
library(tidyverse)
library(magrittr)
library(kableExtra)
library(stargazer)
library(pander)
library(psych)
library(readstata13)
library(knitr)
library(animation)
library(bookdown)
library(rmarkdown)


# Load data 
data <- haven::read_dta("http://staff.washington.edu/phurvitz/csde502_winter_2021/data/AHwave1_v1.dta")
attributes(data$h1gi1m)$labels


```


# Study Overview 

The National Longitudinal Study of Adolescent to Adult Health (Add Health) is a longitudinal study of a nationally representative sample of over 20,000 adolescents who were in grades 7-12 during the 1994-95 school year, and have been followed for five waves to date (https://addhealth.cpc.unc.edu/). This data is from the Add Health Wave 1 data set. 

We will specifically explore poor appetite and depression among adolescents assigned female or male at birth. 



```{r q1, include = F}
### -----------------------------------------------------------
### 

# Create new dataframe 
data_new <- data %>%
  select(aid, bio_sex, h1fs2, h1fs6)


# h1fs2 - You didn’t feel like eating, your appetite was poor.
table(data$h1fs2)
# h1fs6 - You felt depressed.
table(data$h1fs6)


# Set columns to factors
data_new$bio_sex <- as.factor(data_new$bio_sex)
data_new$poor_appetite <- as.factor(data_new$h1fs2)
data_new$depressed <- as.factor(data_new$h1fs6)

levels(data_new$poor_appetite)



```


# Descriptive data

The following tables and graphs show the proportion of females and males reporting poor appetite and depression on a Likert scale. 



```{r q2, echo= F, warning = F, message = F}
### -----------------------------------------------------------
### Create some frequency tables
#a.	Create a frequency table from each variable, using both counts and percentages.


# Tabulate by sex
tab_sex <- data_new %>% 
  group_by(bio_sex) %>%
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate("%" = round(n / sum(n) * 100, 2))


# print the table with better printed names
kable(tab_sex, col.names = c("Sex assigned at bith", "n", "%"), caption = "Distribution of sex assigned at birth") %>% 
    kable_styling(bootstrap_options = 
                      c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, 
                  position = "left")

# Tabulate by poor appetite
tab_poorapp <- data_new %>% 
  group_by(poor_appetite) %>%
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate("%" = round(n / sum(n) * 100, 2))


# print the table with better printed names
kable(tab_poorapp, col.names = c("Reported frequency of poor appetite", "n", "%"), caption = "Distribution of reported poor appetite in the past week") %>% 
    kable_styling(bootstrap_options = 
                      c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, 
                  position = "left")


# Tabulate by depression
tab_depressed <- data_new %>% 
  group_by(depressed) %>%
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate("%" = round(n / sum(n) * 100, 2))


# print the table with better printed names
kable(tab_depressed, col.names = c("Reported frequency of feeling depressed", "n", "%"), caption = "Distribution of reported depression in the past week") %>% 
    kable_styling(bootstrap_options = 
                      c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, 
                  position = "left")

# b.	Create a frequency table based on at least two variables, also with counts and percentages.


# tabulate poor appetite by sex 
tab_app_male <- data_new %>% 
   filter(poor_appetite != "(6) Refused" & poor_appetite != "(8) Don't know") %>% 
    filter(bio_sex == "(1) Male") %>% 
    group_by(poor_appetite) %>% 
    summarise(n = n(), .groups = "drop_last") %>% 
    mutate("%" = round(n / sum(n) * 100, 2))

tab_app_female <- data_new %>% 
   filter(poor_appetite != "(6) Refused" & poor_appetite != "(8) Don't know") %>% 
    filter(bio_sex == "(2) Female") %>% 
    group_by(poor_appetite) %>% 
    summarise(n = n(), .groups = "drop_last") %>% 
    mutate("%" = round(n / sum(n) * 100, 2))


tab_app_sex <- cbind(tab_app_male, tab_app_female)
tab_app_sex[,4] <- NULL

# print the table with better printed names
kable(tab_app_sex, col.names = c("Self-reported Health", "n", "%", "n", "%"), caption = "Reported poor appetite in the past week by sex assigned at birth") %>% 
    kable_styling(bootstrap_options = 
                      c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, 
                  position = "left") %>% 
    add_header_above(c(" " = 1, "Male" = 2, "Female" = 2))


### Create at least one graph from data in the data frame.

#  Barchart
data_new %>%
  filter(bio_sex != "(6) Refused") %>%
  filter(poor_appetite != "(6) Refused" & poor_appetite != "(8) Don't know") %>% 
ggplot(., aes(x=poor_appetite, fill=bio_sex)) + 
  geom_bar(position="fill")+
  theme_classic()+
  ylab("Percentage")+
  xlab("Reported poor appetite in past week")+
  ggtitle("Figure 1. Proportion reported poor appetite in past week by sex assigned at birth")

 
```



# Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
