---
title: "CSDE 502 Winter 2021, Assignment 10"
author: " Taylor Riley [mailto:striley@uw.edu]"
output: 
    bookdown::html_document2:
        number_sections: true
        self_contained: true
        code_folding: hide
        toc: true
        toc_float:
            collapsed: true
            smooth_scroll: false
    pdf_document:
        number_sections: true
        toc: true
        fig_cap: yes
        keep_tex: yes
urlcolor: blue 
---

```{r, include = F}
library(captioner)
library(captioner)
library(kableExtra)
library(stargazer)
library(pander)
library(psych)
library(readstata13)
library(knitr)
library(animation)
library(bookdown)
library(rmarkdown)
library(tidyverse)
library(naniar)


figure_nums <- captioner(prefix = "Figure")
table_nums <- captioner(prefix = "Table")

data <- read.table("../data/Deaths_1x1.txt", skip = 2, header = TRUE)

# Review data
table(data$Year)

```

# Introduction 

Australia, officially named the Commonwealth of Australia, is a sovereign country comprising the mainland of the Australian continent and numerous smaller islands. It is the largest country in Oceania and the world's sixth-largest country by total area. They have kangaroos!

This study will examine sex-specific mortality over time in Australia.


# Methods

## Data

We used data from http://www.mortality.org for Australia. 


## Analysis

We ran a descriptive analysis on total number mortality trends among males and females in Australia from 1921 to 2018. 


# Results


The number of male deaths is always slightly higher than female deaths each year. Total mortality numbers are increasing over time, but this data does not control for population growth. 

```{r, echo = F, message = F, warning = F}

data_new <- data %>%
    group_by(Year) %>%
    summarize(
        sum_female = sum(Female),
        sum_male = sum(Male),
        sum_total = sum(Total))

# Table - deaths by year

# print the table with better printed names
kable(data_new, col.names = c("Year", "Female", "Male", "Total"), caption = "Total deaths in Australia, by sex and total") %>% 
    kable_styling(bootstrap_options = 
                      c("striped", "hover", "condensed", "responsive"), 
                  full_width = F, 
                  position = "left")


# Total deaths 
data_new %>%
    ggplot(aes(x = Year, y=sum_total))+
    geom_point()+
    theme(panel.background = element_rect(fill = 'white', colour = 'black'))+  
  xlab("Year")+
  ylab("Total deaths in Australia")+
  geom_smooth(method = "lm")


# Female deaths 
data_new %>%
    ggplot(aes(x = Year, y=sum_female))+
    geom_point()+
    theme(panel.background = element_rect(fill = 'white', colour = 'black'))+  
  xlab("Year")+
  ylab("Total FEMALE deaths in Australia")+
  geom_smooth(method = "lm")

# Male deaths 
data_new %>%
    ggplot(aes(x = Year, y=sum_male))+
    geom_point()+
    theme(panel.background = element_rect(fill = 'white', colour = 'black'))+  
  xlab("Year")+
  ylab("Total MALE deaths in Australia")+
  geom_smooth(method = "lm")



```


# Discussion 


Total mortality numbers are increasing over time, but this data does not control for population growth. 







# Code Appendix 
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```